Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-04-25 mu/article/article.tex
Alt V^yz layer description completed.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin vel %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:alt-vx-comp-rtp}]
    {\includegraphics[width=\linewidth]{altplots/alt-vxb-rtp-m}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:alt-vy-comp-rtp}]
    {\includegraphics[width=\linewidth]{altplots/alt-vyb-rtp-m}}
    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
    \emph{alt} structure. Both maxima where obtained for a polarization
    angle $\alpha=145^{\circ}$. }
    \label{fig:alt-vab-comp-rtp}
\end{figure}

@@

$|\mathcal{V}^{\mathrm{x}}|$ we can see that for the energy range from 0.70\,eV
to 0.74\,eV all the $xx$, $xy$, and $xz$ components contribute with almost the
same intensity giving a total spin-velocity of 19.3\,Km/s and spin polar and azimuthal angles
$\varphi = 45.8^{\circ}$ and $\theta=40.7^{\circ}$.

@@

Making now the analysis for $|\mathcal{V}^{\mathrm{y}}|$ we have that for the
energy range from 0.70\,eV to 0.74\,eV the $yz$ component have a more intense
response than $yx$ and $yy$ components and they give a total spin-velocity of
51.9\,Km/s and result in polar angle $\varphi=140.7^{\circ}$ and spin azimuthal
angle of $\theta=221.5^{\circ}$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% %%%%%%%%%%%%%%%%%%% |V^{ab}| [0.6:1.0] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
% $\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs.}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{altplots/alt-vxb-rtp.pdf}
%     \includegraphics[width=\linewidth]{altplots/alt-vyb-rtp.pdf}
%     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
%     corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
%     \label{fig:alt-rtp}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{altplots/alt-vyz-layers.pdf}
%     \caption{Layer decomposition for the most intense response:
%     $\mathcal{V}^{\mathrm{yz}}$.}
%     \label{fig:alt-lay}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{altplots/alt-vab-comp.pdf}
%     \caption{Comparisson of the most intense response vs the most intense
%     responses of CdSe and GaAs.}
%     \label{fig:alt-comp}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{altplots/alt-absvab.pdf}
%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$}    
%     \label{fig:alt-xbybcomp}
% \end{figure}

% % subsection alt (end)

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RES UP %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \subsection{Up (graphone)} % (fold)
% \label{sec:results-up}

% %%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.0:0.2] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \subsubsection{$\mathcal{V}^{\mathrm{x}}$ energy range 0.0--0.2 eV }
% \begin{figure}[tb]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-magvxb-incang-1-4545.pdf}
%     \caption{The most intense response for $\mathcal{V}^{\mathrm{x}} $ is for 
%     40$^{\circ}$.}
%     \label{fig:up-magvxbincang1}
% \end{figure}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-vab-xx-angcomp.pdf}
%     \includegraphics[width=\linewidth]{upplots/up-vab-xy-angcomp.pdf}\\
%     \includegraphics[width=\linewidth]{upplots/up-vab-xz-angcomp.pdf}
%     \caption{Cheking angle of incidence for $xb$ components for up structure.}
%     \label{fig:up-xbangcomp}
% \end{figure}
% \begin{figure}[tb]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-vab-xb-1.pdf}
%     \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 40$^{\circ}$.}
%     \label{fig:up-vxb1}
% \end{figure}

% %%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.0:0.2] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \subsubsection{$\mathcal{V}^{\mathrm{y}}$ energy range 0.0--0.2 eV }
% \begin{figure}[tb]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-magvyb-incang-1-4545.pdf}
%     \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
%     40$^{\circ}$.}
%     \label{fig:up-magvybincang1}
% \end{figure}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-vab-yx-angcomp.pdf}
%     \includegraphics[width=\linewidth]{upplots/up-vab-yy-angcomp.pdf}\\
%     \includegraphics[width=\linewidth]{upplots/up-vab-yz-angcomp.pdf}
%     \caption{Cheking angle of incidence for $yb$ components.}
%     \label{fig:up-ybangcomp}
% \end{figure}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-vab-yb-1.pdf}
%     \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 40$^{\circ}$.}
%     \label{fig:up-vyb1}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-absvab-1.pdf}
%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$}    
%     \label{fig:up-xbybcomp-1}
% \end{figure}

% %%%%%%%%%%%%%%%%%%%%%%%%%%% xb [1.8:2.1] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \subsubsection{$\mathcal{V}^{\mathrm{x}}$ energy range 1.8--2.1 eV }

% \begin{figure}[tb]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-magvxb-incang-2-4545.pdf}
%     \caption{The most intense response for $\mathcal{V}^{\mathrm{x}} $ is for 
%     40$^{\circ}$.}
%     \label{fig:up-magxbincang2}
% \end{figure}
% \begin{figure}[tb]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-vab-xb-2.pdf}
%     \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 40$^{\circ}$.}
%     \label{fig:up-vxb2}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-magvyb-incang-2-4545.pdf}
%     \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
%     40$^{\circ}$.}
%     \label{fig:up-magybincang2}
% \end{figure}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-vab-yb-2.pdf}
%     \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 40$^{\circ}$.}
%     \label{fig:upvyb2}
% \end{figure}

% \clearpage

% %%%%%%%%%%%%%%%%%%% |V^{ab}| [0.0:0.2] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
% $\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs for the energy
% range of 0.0--0.2 eV.}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-1.pdf}
%     \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-1.pdf}
%     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
%     corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
%     \label{fig:up-rtp1}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-vyz-layers-1.pdf}
%     \caption{Layer decomposition for the most intense response:
%     $\mathcal{V}^{\mathrm{yz}}$.}
%     \label{fig:up-lay1}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-vab-yz-comp-1.pdf}
%     \caption{Comparisson of the most intense response vs the most intense
%     responses of CdSe and GaAs.}
%     \label{fig:up-comp1}
% \end{figure}

% %%%%%%%%%%%%%%%%%%% |V^{ab}| [1.8:2.1] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
% $\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs for the energy
% range of 1.8--2.1 eV}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-2.pdf}
%     \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-2.pdf}
%     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
%     corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
%     \label{fig:up-rtp2}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-vyz-layers-2.pdf}
%     \caption{Layer decomposition for the most intense response:
%     $\mathcal{V}^{\mathrm{yz}}$.}
%     \label{fig:up-lay2}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-vab-yz-comp-2.pdf}
%     \caption{Comparisson of the most intense response vs the most intense
%     responses of CdSe and GaAs.}
%     \label{fig:up-comp2}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-absvab-2.pdf}
%     % \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$}    
%     \label{fig:up-xbybcomp-2}
% \end{figure}

% % subsection up (end)

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% AA %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \subsection{HNBC$_{2}$H-aa} % (fold)
% % \label{sec:results-aa}

% %%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$\mathcal{V}^{\mathrm{x}} $}
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-magvxb-incang-4545.pdf}
%     \caption{The most intense response for $\mathcal{V}^{\mathrm{x}} $ is for 
%     155$^{\circ}$.}
%     \label{fig:aa-magvxbincang}
% \end{figure}
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vxx.pdf}
%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vxy.pdf}\\
%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vxz.pdf}
%     \caption{Cheking angle of incidence for $xb$ components. There is a
%     different angle for each component to have the most intense response.}
%     \label{fig:aa-xbangcomp}
% \end{figure}
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-magvxb.pdf}
%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ for different
%     polarization angles.}
%     \label{fig:aa-magvxb}
% \end{figure}
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vxb-1.pdf}
%     \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 155$^{\circ}$.}
%     \label{fig:aa-vxb1}
% \end{figure}

% \clearpage

% %%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$\mathcal{V}^{\mathrm{y}} $}
% \begin{figure}[h!]
%     \centering
%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-magvyb-incang-4545.pdf}
%     \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
%     155$^{\circ}$.}
%     \label{fig:aa-magvybincang}
% \end{figure}
% \begin{figure}[h!]
%     \centering
%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vyx.pdf}
%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vyy.pdf}\\
%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vyz.pdf}
%     \caption{Cheking angle of incidence for $yb$ components. There is a
%     different angle for each component to have the most intense response.}
%     \label{fig:aa-ybangcomp}
% \end{figure}
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-magvyb.pdf}
%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{y}}|$ for different
%     polarization angles.}
%     \label{fig:aa-magvyb}
% \end{figure}
% \begin{figure}[t!]
%     \centering
%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vyb-2.pdf}
%     \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 175$^{\circ}$.}
%     \label{fig:aa-vyb2}
% \end{figure}

% \clearpage

% %%%%%%%%%%%%%%%%%%% |V^{ab}| [0.5:3.0] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
% $\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs.}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vxb-rtp.pdf}
%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vyb-rtp.pdf}
%     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
%     corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
%     \label{fig:aa-rtp}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vyx-layers.pdf}
%     \caption{Layer decomposition for the most intense response:
%     $\mathcal{V}^{\mathrm{yz}}$.}
%     \label{fig:aa-lay}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vab-comp.pdf}
%     \caption{Comparisson of the most intense response vs the most intense
%     responses of CdSe and GaAs.}
%     \label{fig:aa-comp}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-absvab.pdf}
%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$.}    
%     \label{fig:aa-xbybcomp}
% \end{figure}

% % subsection aa (end)

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% AB %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \subsection{HNBC$_{2}$H-ab} % (fold)
% \label{sec:results-ab}

% \begin{figure}[tb]
%     \centering
%     \includegraphics[width=\linewidth]{../hnbGh-ab/hnbGh-ab-figures/hnbGh-ab-1}
%     \includegraphics[width=\linewidth]{../hnbGh-ab/hnbGh-ab-figures/hnbGh-ab-2}
%     \caption{HNBC$_{2}$H-ab structure}
%     \label{fig:abstruc}
% \end{figure}

% %%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$\mathcal{V}^{\mathrm{x}} $}
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-magvxb-incang-4545.pdf}
%     \caption{The most intense response for $\mathcal{V}^{\mathrm{x}} $ is for 
%     155$^{\circ}$.}
%     \label{fig:ab-magvxbincang}
% \end{figure}
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vxx.pdf}
%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vxy.pdf}\\
%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vxz.pdf}
%     \caption{Cheking angle of incidence for $xb$ components. There is a
%     different angle for each component to have the most intense response.}
%     \label{fig:ab-xbangcomp}
% \end{figure}

% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-magvxb.pdf}
%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ for different
%     polarization angles.}
%     \label{fig:ab-magvxb}
% \end{figure}
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vxb.pdf}
%     \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 155$^{\circ}$.}
%     \label{fig:ab-vxb}
% \end{figure}

% \clearpage

% %%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$\mathcal{V}^{\mathrm{y}} $}
% \begin{figure}[h!]
%     \centering
%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-magvyb-incang-4545.pdf}
%     \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
%     155$^{\circ}$.}
%     \label{fig:ab-magvybincang}
% \end{figure}
% \begin{figure}[h!]
%     \centering
%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vyx.pdf}
%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vyy.pdf}\\
%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vyz.pdf}
%     \caption{Cheking angle of incidence for $yb$ components. There is a
%     different angle for each component to have the most intense response.}
%     \label{fig:ab-ybangcomp}
% \end{figure}

% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-magvyb.pdf}
%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{y}}|$ for different
%     polarization angles.}
%     \label{fig:ab-magvyb}
% \end{figure}
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vyb.pdf}
%     \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 125$^{\circ}$.}
%     \label{fig:ab-vyb}
% \end{figure}

% \clearpage

% %%%%%%%%%%%%%%%%%%% |V^{ab}| [0.5:3.0] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
% $\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs.}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vxb-rtp.pdf}
%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vyb-rtp.pdf}
%     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
%     corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
%     \label{fig:ab-rtp}
% \end{figure}

% % \begin{figure}[ht]
% %     \centering
% %     \includegraphics[width=\linewidth]{}
% %     \caption{Layer decomposition for the most intense response:
% %     $\mathcal{V}^{\mathrm{yz}}$.}
% %     \label{fig:ab-lay}
% % \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vab-comp.pdf}
%     \caption{Comparisson of the most intense response vs the most intense
%     responses of CdSe and GaAs.}
%     \label{fig:ab-comp}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{abplots/hnbGh-absvab.pdf}
%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$.}    
%     \label{fig:ab-xbybcomp}
% \end{figure}

% % subsection ab (end)

% section results (end)

@@

\section{Fixing velocity} % (fold)
\label{sec:fixing_velocity}

\begin{equation}
\mathcal{V}^\mathrm{a}_{\sigma} 
= 
\sqrt{
\mathcal{V}^\mathrm{ax} + 
\mathcal{V}^\mathrm{ay} +
\mathcal{V}^\mathrm{az}
}
\end{equation}

\begin{equation}
\mathcal{V}^\mathrm{a}_{\sigma\parallel} 
= 
\sqrt{
\mathcal{V}^\mathrm{ax} + 
\mathcal{V}^\mathrm{ay} 
}
\end{equation}

\begin{align}
\theta_{a} 
&=
\sin^{-1}
\left( 
\frac{\mathcal{V}^\mathrm{a}_{\sigma\parallel}}
{\mathcal{V}^\mathrm{a}_{\sigma}}
\right)
\\
\varphi_{a} 
&=
\sin^{-1}
\left(
\frac{\mathcal{V}^\mathrm{ay}}{\mathcal{V}^\mathrm{a}_{\sigma\parallel}}
\right)
\end{align}

% section fixing_velocity (end)

\section{Fixing spin} % (fold)
\label{sec:fixing_spin}

% section fixing_spin (end)

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin vel Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:alt-vx-comp-rtp}]
    {\includegraphics[width=\linewidth]{altplots/alt-vxb-rtp-m}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:alt-vy-comp-rtp}]
    {\includegraphics[width=\linewidth]{altplots/alt-vyb-rtp-m}}
    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
    \emph{alt} structure. Both maxima where obtained for a polarization
    angle $\alpha=145^{\circ}$. }
    \label{fig:alt-vab-comp-rtp}
\end{figure}

@@

$|\mathcal{V}^{\mathrm{x}}|$ depicted in Fig. \ref{fig:alt-vx-comp-rtp} we can
see that for the energy range from 0.70\,eV to 0.74\,eV all the $xx$, $xy$, and
$xz$ components contribute with almost the same intensity giving a total spin-
velocity of 19.3\,Km/s and spin polar and azimuthal angles $\varphi =
45.8^{\circ}$ and $\theta=40.7^{\circ}$.

@@

Making now the analysis for $|\mathcal{V}^{\mathrm{y}}|$ depicted in Fig.
\ref{fig:alt-vy-comp-rtp} we have that for the energy range from 0.70\,eV to
0.74\,eV the $yz$ component have a more intense response than $yx$ and $yy$
components and they give a total spin-velocity of 51.9\,Km/s and result in polar
angle $\varphi=140.7^{\circ}$ and spin azimuthal angle of
$\theta=221.5^{\circ}$.

@@

\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:alt-vx-lay}]
    {\includegraphics[width=\linewidth]{figures/blank}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:alt-vy-lay}]
    {\includegraphics[width=\linewidth]{figures/blank}}
    \caption{Layer-by-layer contribution of $|\mathcal{V}^{\mathrm{x}}|$ and
    $|\mathcal{V}^{\mathrm{y}}|$ for a polarization angle $\alpha=145^{\circ}$
    for the \emph{alt} structure.}
    \label{fig:alt-vab-lay}
\end{figure}
\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vyz-layers}
    \caption{Layer-by-layer contribution of $\mathcal{V}^{\mathrm{yz}}$ for the
     \emph{alt} structure.}
    \label{fig:alt-vyz-lay}
\end{figure}

% %%%%%%%%%%%%%%%%
% %% Description of ALT layer |V^{ab}|
% %% files: 
% %%%%%%%%%%%%%%%%
In Fig. \ref{fig:alt-vab-lay} we show the layer-by-layer contribution of
$|\mathcal{V}^{\mathrm{ab}}|$  for the \emph{alt} structure. The corresponding
layer division and atom types and positions are presented in Table 
% 
\ref{tab:alt-unitcell} and depicted in Fig. \ref{fig:alt-struc}. In the layer-
by-layer contribution for $|\mathcal{V}^{\mathrm{x}}|$ (Fig. \ref{fig:alt-vx-lay})
we have that
% 
\textcolor{red}{\ldots}
% 
Also, for the layer-by-layer contribution for $|\mathcal{V}^{\mathrm{y}}|$ (Fig.
\ref{fig:alt-vy-lay}) we have that
% 
\textcolor{red}{\ldots}
%
% %%%%%%%%%%%%%%%%
% %% Description of ALT layer |V^{yz}|
% %% files:  v.sm_0.03_yz_14452_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_1_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_2_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_3_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_4_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_5_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_6_65-spin_scissor_0_Nc_32_ang_145
% %%         alt-plots/alt-vab-layers.gp
% %%%%%%%%%%%%%%%%
From the bottom panels of Fig. \ref{fig:alt-vab-comp-rtp} we can see that for
the \emph{alt} structure the most intense component of
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ corresponds to
$\mathcal{V}^{\mathrm{yz}}$ which has a value of -40.21374498\,Km/s for an
energy incident beam of 0.72\,eV. This component and the corresponding layer by
layer contribution is depicted in Fig. \ref{fig:alt-vyz-lay}. From this figure
we have that for the energy range from 0.70\,eV to 0.74\,eV the fifth and sixth
layers corresponding to the bottom carbon and hydrogen numbered with 5 and 6 in
Fig. \ref{fig:alt-struc} have contributions in opposite direction than the other
4 layers resulting in a total response $\mathcal{V}^{\mathrm{yz}}= -40.2$\,Km/s
for an incoming beam energy of 0.72\,eV. In the other hand, for the energy range
from 0.88\,eV to 0.95\,eV the response for the all six layers the responses are
in the same direction resulting in a total response
$\mathcal{V}^{\mathrm{yz}}=-32.89$\,Km/s for an incoming beam with energy of
0.912\,eV.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin vel Up  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Fixing spin} % (fold)
\label{sec:res-fixspin}

% subsection res-fixspin (end)

@@
